On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-09 Manuscript/manuscript.tex
Small Edits in Reply

\subsection*{Marginal Unit Exponential Distribution}
Additionally, to investigate if the results are robust to nonnormal
marginal distributions, we evaluated the performance of block
bootstrap for a time series with a non-normal marginal
distribution. Specifically, we estimated the mean, standard deviation,
and the lag-1 autocorrelation coefficient of a stationary series with
marginal unit exponential distribution. Note that we expect the CIs
that are based on bootstrap ``tables" to depend on the 
asymptotic distribution of the estimator.  This asymptotic
distribution depends more on the sample size than on the marginal
distribution of the time series. So we expect such CIs to 
have similar performance for different marginal distributions when the
sample sizes is large.  The percentile-based CIs (Percentile, BC, BCA,
Recentered Percentile CI) are not necessatily expected to perform
better under non-normal marginal distributions. The student's t and
and normal-based CIs are only noticeably different when the number of
blocks is smaller than 20.

>>>>

\subsection*{Marginal Unit Exponential Distribution}
Additionally, to investigate if the results are robust to nonnormal
marginal distributions, we evaluated the performance of block
bootstrap for a time series with a non-normal marginal
distribution. Specifically, we estimated the mean, standard deviation,
and the lag-1 autocorrelation coefficient of a stationary series with
marginal unit exponential distribution. Note that we expect the CIs
that are based on bootstrap ``tables" to depend on the 
asymptotic distribution of the estimator.  This asymptotic
distribution depends more on the sample size than on the marginal
distribution of the time series. So we expect such CIs to 
have similar performance for different marginal distributions when the
sample sizes is large.  The percentile-based CIs (Percentile, BC, BCA,
Recentered Percentile) are not necessarily expected to perform
better under non-normal marginal distributions. The student's t and
and normal-based CIs are only noticeably different when the number of
blocks is smaller than 20.

### 2024-01-09 Manuscript/reply.tex
Small Edits in Reply

Thank you for this suggestion. The motivation behind the proposed
recentered CI is that. for the autocorrelation parameter in the
simulation studies, the centers of the existing CIs appeared to be a
biased estimator of the target while the spreads of the CIs still
provide good uncertainty measures. This has now been added in the
Recentered Percentile CI paragraph.

@@

Thank you for the suggestion idea. We have reformatted all of our coverage rate plots 
accordingly, which has saved a lot of space!

@@

Thank you for the comment. We expect the CIs that 
are based on bootstrap ``tables" to depend on the 
asymptotic distribution of the point estimator. This asymptotic
distribution depends more on the sample size than on the marginal
distribution of the time series. So we expect such CIs to 
have similar performance for different marginal distributions when the
sample sizes is large.  The percentile-based CIs (Percentile, BC, BCA,
Recentered Percentile CI) are not necessatily expected to perform
better under non-normal marginal distributions. The student's t and
and normal-based CIs are only noticeably different when the number of
blocks is smaller than 20. We have added a discussion on this point in
the first paragraph of the subsection of Marginal Unit Exponential
Distribution.

@@

Thank you for pointing this out. We tried both Wald intervals and exact 
Clopper-Pearson intervals. Although we did not find a major difference between
the two, we have switched to Clopper-Pearson intervals to avoid the potential
undercoverage.

@@

We have discussed this in the third paragraph of the Marginal Standard Normal 
Distribution subsection of the Design section, and we have provided a reference
for Clopper-Pearson intervals \citep{clopper1934use} as well as the package we 
used \citep{PropCIs}.

@@

Thank you for the suggestion. However, because of the deterioration for $\phi$, 
we found it hard to fix the limits on the 
y-axis without hurting the visualization for the other rows. 
Figure~\ref{fig:alt2_norm1} is provided as an example:

@@

Thank you for this comment.
A possible explanation for this is that if a 
stationary series has a positive 
autocorrelation, the effective sample
size is decreased, whereas is a series has a negative autocorrelation, the
effective sample size is increased. Additionally, this seems to have a 
greater effect on the the estimation of the location parameter versus that
of the scale parameter or temporal dependence parameter. We have included a 
similar
comment at the end of the paragraph on estimation of~$\mu$, and we provided a 
reference for effective sample size \citep{geyer2011introduction}.

@@

Thank you for the comment. We only
used serial dependences as strong as 0.4, because we only seek to 
establish the 
general trend as the strength of the autocorrelation 
increases, and how it varies depending on the sign of the autocorrelation and 
the parameter of interest. This justification has been added to the Design 
section. We have also added a deliberation (third paragraph in the Discussion) 
regarding what would
be expected for higher dependence levels.
\jy{give the location of the paragraph in the text.}
\mc{addressed}

@@

Thank you for the comment. We have included a discussion of problems 
with block bootstrap in the introduction, while also highlighting its advantages
which motivated this investigation into their CI performance. This
last sentences of the manuscript has also been rewritten to call for
understanding of the subpar performance of the existing
percentile-based CIs for the autocorrelation parameter and situations
where the proposed CI should be recommended.

>>>>

Thank you for this suggestion. The motivation behind the proposed
recentered CI is that for the autocorrelation parameter in the
simulation studies, the centers of the existing CIs appeared to be a
biased estimator of the target while the spreads of the CIs still
provide good uncertainty measures. This has now been added in the
Recentered Percentile CI paragraph.

@@

Thank you for the suggested idea. We have reformatted all of our coverage rate 
plots 
accordingly, which has saved a lot of space!

@@

Thank you for the comment. We expect the CIs that 
are based on bootstrap ``tables" to depend on the 
asymptotic distribution of the point estimator. This asymptotic
distribution depends more on the sample size than on the marginal
distribution of the time series. So we expect such CIs to 
have similar performance for different marginal distributions when the
sample sizes is large.  The percentile-based CIs (Percentile, BC, BCA,
Recentered Percentile) are not necessarily expected to perform
better under non-normal marginal distributions. The student's t and
and normal-based CIs are only noticeably different when the number of
blocks is smaller than 20. We have added a discussion on this point in
the first paragraph of the Marginal Unit Exponential
Distribution subsection.

@@

Thank you for pointing this out. We tried both Wald intervals and exact 
Clopper-Pearson intervals. Although we did not find a major difference between
the two, we have switched to Clopper-Pearson intervals to avoid the potential
undercoverage. We have discussed this in the third paragraph of the Marginal 
Standard Normal 
Distribution subsection of the Design section, and we have provided a reference
for Clopper-Pearson intervals \citep{clopper1934use} as well as the package we 
used \citep{PropCIs}.

@@

@@

Thank you for the suggestion. However, because of the deterioration for $\phi$, 
we found it hard to fix the limits on the 
y-axis without hurting the visualization for the other rows. The other reviewer
suggested that we put the 6 figures in a column in 
a single plot.
Figure~\ref{fig:alt2_norm1} is provided as an example of this with fixed limits:

@@

Thank you for this comment.
A possible explanation for this is that if a 
stationary series has a positive 
autocorrelation, the effective sample
size is decreased, whereas is a series has a negative autocorrelation, the
effective sample size is increased. Additionally, this seems to have a 
greater effect on the the estimation of the location parameter versus that
of the scale parameter or temporal dependence parameter. We have included a 
comment at the end of the paragraph on estimation of~$\mu$, and we provided a 
reference for effective sample size \citep{geyer2011introduction}.

@@

Thank you for the comment. We only
used serial dependences as strong as 0.4, because we only seek to 
establish the 
general trend as the strength of the autocorrelation 
increases, and how it varies depending on the sign of the autocorrelation and 
the parameter of interest. This justification has been added to the first
paragraph of the Normal section of the Design 
section. We have also added a deliberation (third paragraph in the Discussion) 
regarding what would
be expected for higher dependence levels.
\jy{give the location of the paragraph in the text.}
\mc{addressed}

@@

Thank you for the comment. We have included a discussion of problems 
with block bootstrap as the second paragraph in the introduction, while also 
highlighting its advantages
which motivated this investigation into their CI performance. This
last few sentences of the manuscript have also been rewritten to call for
understanding of the subpar performance of the existing
percentile-based CIs for the autocorrelation parameter and situations
where the proposed CI should be recommended.
